---
title: "<b>University Canteen Survey</b>"
author: "I Kadek Defa Danuarta"
output:
  html_document: default
  pdf_document: default
 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# **Backgrounds**  
I'm as the team member of students participating in a university mobility program. During this program, we conducted a project analyzing student satisfaction with the campus cafeteria. In this project, I will attempt to analyze perceptions of service, cleanliness, and food quality, and to identify factors influencing overall satisfaction.

# **Datasets**{.tabset}  
The dataset was collected from an internal university survey measuring student satisfaction with cafeteria services, cleanliness, and food products. Responses were gathered anonymously using a Likert scale questionnaire.

***DISCLAIMER***\
For confidentiality, campus names and identifiers have been anonymized (e.g., 'Campus s', 'Campus b'). No personal identity information (such as names, student IDs, or emails) was included.

<!-- Importing Library -->

```{r importing-lib}
library(ggplot2)
library(plotly)
library(dplyr)
library(tidyr)
library(readxl)
library(knitr)
library(DT)
library(lubridate) #to process the time stamp
```

<!-- Importing Dataset -->

```{r import-data}
dirty_df <- read_excel("questionaire_result.xlsx")
```

## **Data Cleaning & Preprocessing**

```{r missing-value, results = 'hide'}
# this code is used to see all the missing value in each columns
colSums(is.na(dirty_df))
```

### **Identifies Missing Value and The Causes**

```{r viewing-missing-value}
na_count <- colSums(is.na(dirty_df))
na_cols <- names(na_count[na_count > 0])

cat("Missing values is founded in:\n")
for (col in na_cols) {
  cat(col, ":", na_count[col], "missing value(s)\n")
}
```

The main reason for the missing values, especially for *Home Campus*, is that the respondents are not active participants in the mobility program. Since the purpose is to measure the satisfaction of **students who are actively involved in the mobility program**, I decided to remove these entries with missing *Home Campus* values.

For column **major**, I imputed the missing values using the most frequently occurring major. This approach is intended to preserve useful responses, as the remaining data may still contribute valuable insights for the analysis.

<!-- **Deleting Missing Values** -->

```{r deleting-missing-value, results = 'hide'}
df <- na.omit(dirty_df)

sum(is.na(df$home_campus))
```

<!-- **Imputing Missing Value For "major"** -->

```{r impute-major, results='hide'}
get_mode <- function(v) {
  uniqv <- na.omit(unique(v))
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

df$major[is.na(df$major)] <- get_mode(df$major)
```

<!-- Viewing result -->

```{r}
new_na_count <- colSums(is.na(df))
na_cols <- names(new_na_count[new_na_count > 0])

cat("Missing values after deletion and imputation:\n")
cat("major:", sum(is.na(df$major)), "\n")
cat("home_campus:", sum(is.na(df$home_campus)))
```

From the results above it shows a successful attemp to handle missing values

### **Deleting Irrelevant Column**  
Since this analysis focusing on the result of likert scales, it'll be necessarily to delete some advice column to keep the analysis on track\
```{r deleting-irrelevant-column}
deleted_column <- c("advice_for_services", "cleanliness_advice", "facility_advice", "product_advice")

df <- df %>% 
  select(-deleted_column)
```


### **Handle Inconsistent Values in Likert Scale**

```{r insert-likert-column, results='hide'}
#likert columns
likert_cols <- df %>% select(where(is.character), 
                             -c(major, 
                                active_mobility, 
                                home_campus, 
                                frequency_visiting_canteen
                                )) %>% names()
```

To anticipate inconsistent values, I'll change all the likert categories to a lowercase (in case there are some miss type in the questionnaire form)

```{r mutate-inconsistent-likert}
cat("Before mutation:", paste(unique(df$staff_response), collapse = ", "), "\n")

#get every categorical column
cat_cols <- df %>%select(where(is.character)) %>% names()

#mutate every category to lowercase
df <- df %>% mutate(across(all_of(cat_cols), ~ tolower(.)))

#make a copy of dataframe to be extracted in csv format
export_mutated_df <- df
write.csv(export_mutated_df, "1st_cleaned_mutated_questionnaire_results.csv", row.names = FALSE)

cat("After mutation:", paste(unique(df$staff_response), collapse = ", "))
```

This process is to anticipate errors in encoding process, since the inconsistent value is completely handled, encoding is needed to transform the likert category to a numeric form of scale.

### **Separating Date, Timestamp, and Durations**

```{r separating-time-date-dur, results='hide'}
#make a temporary dataframe to obtain the date and time
selected_time_col <- c("start_time", "completion_time")
temporary <- df[selected_time_col]

#extract date
temporary$date <- as.Date(df$start_time)

#extract start time and finish
temporary$started_time <- format(df$start_time, "%H:%M:%S")
temporary$finished_time <- format(df$completion_time, "%H:%M:%S")

#calculate duration in minutes
temporary$durations <- as.numeric(difftime(temporary$completion_time, df$start_time, units = "mins") %>% round(digits = 2))

df$date <- temporary$date
df$start_time <- temporary$started_time
df$completion_time <- temporary$finished_time
df$duration <- temporary$durations
```

```{r view-date}
#head(temporary %>% select(start_time, completion_time))
datatable(temporary %>% select(start_time, completion_time), caption = "Default Timestamp")
```

By default, the tool used to gather questionnaire results has a time stamp about starting time to a completion time. Where in this case I will parse them to an identical column. In this case I'll separate the date and time into an individual column.

```{r view-separated-date}
#head(df %>% select(ID, major, date, start_time, completion_time, duration))
datatable(df %>% select(ID, major, date, start_time, completion_time, duration), caption = "Separated Timestamp")
```

### **Encoding Likert Scale and frequency**

```{r viewing-unique-value}
#cat("Unique value for frequency of respondent visit canteen: ", paste(unique(df$frequency_visiting_canteen), collapse = ", "), "\n")
cat("Unique value for every likert scale: ", paste(unique(df$friendly_staff), collapse = ", "))
```

The result above are unique values. Where in this case, every likert scales will be encoded manually to a range number from one(1) to five(5).

```{r encode-likert-freq}
#scales
likert_scale <- c("sangat tidak setuju", "tidak setuju", "tidak merasakan", "setuju", "sangat setuju")
df[likert_cols] <- lapply(df[likert_cols], function(col) match(col, likert_scale))

#freq
#frequency <- c("0 kali", "1-2 kali", "3-4 kali", ">4 kali")
#df$frequency_visiting_canteen <- sapply(df$frequency_visiting_canteen, function(freq) match(freq, frequency))


#Export dataframes to csv file
export_encoded_df <- df
write.csv(export_encoded_df, "2nd_encoded_questionnaire_results.csv", row.names = FALSE)


#cat("Unique value for frequency of respondent visit canteen: (after encoding)", paste(unique(df$frequency_visiting_canteen), collapse = ", "), "\n")
cat("Unique value for every likert scale (after encoding): ", paste(unique(df$friendly_staff), collapse = ", "))
```

### **New Column for Further Analysis**

```{r calc-mean-satisfaction}
df$mean_satisfaction_score <- rowMeans(df[likert_cols], na.rm = TRUE)
```

**Average/Mean Satisfaction Score**\
Here I make a new column to support further analysis and prediction tasks. This value is calculated as the **average of every encoded likert scale**. Why is this important? it provides a single quantitative measure that summarizes overall student satisfaction. It allows for easier comparison between respondents and can be used as a target variable in predictive modeling or segmentation analysis.

```{r calc-mean-score-per-aspects}
#take every column based on their aspects
cols_services <- c("staff_response", 
                   "friendly_staff", 
                   "quick_response_staff", 
                   "order_waiting_time", 
                   "payment_method", 
                   "smooth_payment", 
                   "clear_menu_info")
cols_cleanliness <- c("clean_area", 
                      "cozy_room_layout", 
                      "neat_furniture_placement", 
                      "clean_utensils", 
                      "cleaning_facility", 
                      "proper_table_chair", 
                      "cozy_seating_area") 
cols_product <- c("menu_variety",
                  "healty_menu",
                  "freshness_menu",
                  "taste_match_price",
                  "affordable_price", 
                  "price_vs_quality")
df$mean_services_score <- rowMeans(df[cols_services], na.rm = TRUE) %>% round(digits = 2)
df$mean_cleanliness_score <- rowMeans(df[cols_cleanliness], na.rm = TRUE) %>% round(digits = 2)
df$mean_product_score <- rowMeans(df[cols_product], na.rm = TRUE) %>% round(digits = 2)

#head(df %>% select(ID, major, mean_services_score, mean_cleanliness_score, mean_product_score, mean_satisfaction_score))
datatable(df %>% select(ID, major, mean_services_score, mean_cleanliness_score, mean_product_score, mean_satisfaction_score), caption = "Score per Aspects")

#export to csv file
export_scores_df <- df
write.csv(export_scores_df, "3rd_avg_scores_added_questionnaire_results.csv", row.names = FALSE)
```

**Average/Mean Score in Every aspects**\
To perform an in-depth analysis of the performance of each metric measured such as services, cleanliness, and product, I created a new column to store the average of each question to measure respondents' satisfaction with the aspects

## **Analysis**

### **Distribution of Duration**

The first analysis is to see the distribution of duration. This graph might help to evaluate respondents who fill out the questionnaire too quickly or too slowly, which indicates their seriousness in answering the questionnaire.

```{r distribution-of-duration}
plot_duration_dist <- ggplot(df, aes(x = duration, y = ))+
  geom_histogram(fill = "#B4E50D")+
  labs(
    title = "Distribution of Duration (minutes)",
    x = "Durations"
  )+
  theme_classic()
#show(plot_duration_dist)
ggplotly(plot_duration_dist)
```

Based on the histogram above, respondents are more likely to complete the questionnaire in about 2 minutes. This data shows that respondents answered the questionnaire fairly quickly.

At 0 minutes, this could be caused by some respondents answered the questionnaire very quickly and might not read the questions (not taking it seriously). Further analysis will be explained through the descriptive statistics below.

```{r stat-desc-duration}
summary(df$duration)
```

The shortest duration for respondent to fill questionnaire is 0.520 minutes.

### **Canteen Visitors Frequency**{.tabset}

In this analysis, I'll try to measure visitation rate with satisfaction. In order to categorize the satisfaction level, I'll use discretization or binning to make a category out of mean satisfaction score. The mapping of this process are as follows:

***(MSS = Mean Satisfaction Score)***

-   MSS less or equal to 1 = "Bad"\
-   MSS greater than 1 AND MSS less or equal to 3 = "Quite Bad"\
-   MSS greater than 3 AND MSS less than 5 = "Good"\
-   MSS equal to 5 = "Excellent"  

```{r binning-mean-satisfaction-score, results='hide'}
df <- df %>% 
  mutate(satisfaction_category = case_when(
    mean_satisfaction_score <= 1 ~ "Bad",
    mean_satisfaction_score > 1 & mean_satisfaction_score <= 3 ~ "Quite Bad",
    mean_satisfaction_score > 3 & mean_satisfaction_score < 5 ~ "Good",
    mean_satisfaction_score == 5 ~ "Excellent"
  ))

#export to csv file
export_binning_scores_df <- df
write.csv(export_binning_scores_df, "4th_binning_scores_added_questionnaire_results.csv", row.names = FALSE)
```

#### **Graph View**  

After discretization or binning process, the analysis will be utilizing a plot to show the **Amount of Canteen Visitors by Frequent Visiting and Satisfaction Category**

```{r frequency-canteen-visitors}
freq_canteen_visit_scheme <- c(
  "Bad" = "#F93827",
  "Quite Bad" = "#FF9D23",
  "Good" = "#B4E50D",
  "Excellent" = "#78C841"
) 

plot_freq_canteen_visit <- ggplot(df, aes(x = frequency_visiting_canteen, fill = satisfaction_category))+
  geom_bar()+
  labs(
    title = "Canteen Visitors by Frequent Visiting and Satisfaction Category",
    x = "Frequency Category"
  )+
  scale_fill_manual(values = freq_canteen_visit_scheme)+
  theme_classic()

#show(plot_freq_canteen_visit)
ggplotly(plot_freq_canteen_visit)
```

***Explanation:***

-   The visitors mostly come once until two times a week, meaning that the canteen is not a frequent place to visit. The overall satisfaction level is on "good" condition with 2 respond show an excellent satisfaction level.\
-   Respondent who chose "0 kali" or rarely go to canteen showing the most "quite bad" satisfaction level among others. This might indicated by some people that had a unfulfilled expectations.

#### **Table View**  
```{r viewing-binning-result}
#head(df %>% select(ID, major, mean_satisfaction_score, satisfaction_category))
datatable(df %>% select(ID, major, frequency_visiting_canteen, mean_satisfaction_score, satisfaction_category), caption = "Binning Mean Satisfaction Score Result")
```

### **Performances in every aspects**

This analysis is conducted to know the performance of every aspects that measured. The aspects that are measured such as, service, cleanliness, and product. The graph below shows the total average of the average performance scores for each aspect. This graph is expected to provide an overview of aspects that can be improved in the University cafeteria.\

```{r performance-total-mean-aspects}
#calculate the total mean of every aspects
aspect_mean_score <- df %>% 
  summarize(
    services = mean(mean_services_score, na.rm= TRUE),
    cleanliness = mean(mean_cleanliness_score, na.rm= TRUE),
    product = mean(mean_product_score, na.rm= TRUE),
  )

#turn the "means" to long format
aspect_mean_score_long <- pivot_longer(aspect_mean_score, everything(), names_to = "Aspect", values_to = "mean_score")

#binning to tell the color identity
aspect_mean_score_long <- aspect_mean_score_long %>% 
  mutate(
    Performance = case_when(
      mean_score > 4 ~ "Good",
      mean_score >= 3.9 ~ "Medium",
      TRUE ~ "Needs Improvement"
    )
  )

#make a color scheme
peformance_ttl_mean_scheme <- c(
  "Needs Improvement" = "#FF9D23",
  "Medium" = "#B4E50D",
  "Good" = "#78C841"
) 

plot_peformance_ttl_mean <- ggplot(aspect_mean_score_long, aes(x = Aspect, y = mean_score, fill = Performance))+
  geom_bar(stat = "identity", width = 0.6)+
  geom_text(aes(label = round(mean_score, 2)), vjust = -0.5, size = 4)+
  labs(
    title = "Total Average Canteen Score per Aspect",
    x = "Aspects",
    y = "Mean Score"
  )+
  ylim(0, 5) +
  scale_fill_manual(values = peformance_ttl_mean_scheme)+
  theme_minimal()

#show(plot_peformance_ttl_mean)
ggplotly(plot_peformance_ttl_mean)
```
***Explanation***

-   Based on the graph above, respondents gave **fairly good responses to the service**, as indicated by the average total score falling into the “good” category.\
-   This was followed by the performance of the canteen food, which received a “medium” rating, with **room for improvement in terms of product quality and price.**\
-   Finally, the aspect of **cleanliness requires significant improvement** in terms of cleanliness and access to washing facilities.


### **Seeing the Weaknesses of each Aspect**{.tabset}  
In this analysis, I will focus on aspects that have a “Need Improvements” status which referring to Product and Cleanliness aspect. Here, I will create a descriptive statistical table to dig deeper into the areas that are weaknesses that greatly affect the average student satisfaction score for the University cafeteria.  

In this process, it'll require binning technique to categorize each variables based on their average scores. The Binning process will be mapped as follows:

-   mean less than 3.5 = "Needs Improvement"  
-   mean less than 4 = "Medium"  
-   mean greater than or equal 4 = "Good"  

```{r identify-weaknesses-aspect}
#each of the variables name is already declared

#make a long df to combine the multiple column to an each identical column per aspects
df_long_stats <- df %>% 
  select(all_of(c(cols_services, cols_cleanliness, cols_product))) %>%
  pivot_longer(cols = everything(),
               names_to = "variable",
               values_to = "score") %>%
  mutate(aspect = case_when(
    variable %in% cols_services ~ "service",
    variable %in% cols_cleanliness ~ "cleanliness",
    variable %in% cols_product ~ "product"
  ))

#count the stats
df_stats <- df_long_stats %>% group_by(aspect, variable) %>%
  summarise(
    #I'll round the result to handle the numbers with ease
    mean = mean(score, na.rm = TRUE) %>% round(digits = 4),
    median = median(score, na.rm = TRUE),
    sd = sd(score, na.rm = TRUE) %>% round(digits = 4),
    max = max(score, na.rm = TRUE),
    min = min(score, na.rm = TRUE)
  )

#binning
df_stats <- df_stats %>% mutate(
  category = case_when(
    mean < 3.5 ~ "Needs Improvement",
    mean < 4 ~ "Medium",
    TRUE ~ "Good"
  )
)
```

#### **Graph View**  
```{r extract-stats, results='hide'}
#extract every variable to a new df based on their aspect
services_df <- df_stats %>% filter(aspect =="service")
cleanliness_df <- df_stats %>% filter(aspect =="cleanliness")
product_df <- df_stats %>% filter(aspect =="product")
```

```{r cleanliness-stat-plot}
plot_clean_stat <- ggplot(cleanliness_df, aes(x = variable, y = mean, fill = category))+
  geom_col() +
  coord_flip() +
  facet_wrap(~ aspect, scales = "free_y") +
  labs(title = "Average Score per Variable on Cleanliness Aspect",
       x = "Variable", y = "Mean Score") +
  scale_fill_manual(values = c("Needs Improvement" = "#FF9D23", 
                               "Medium" = "#B4E50D", 
                               "Good" = "#78C841")) +
  theme_minimal()
  
ggplotly(plot_clean_stat)
#show(plot_clean_stat)
```

##### **Cleanliness**  
The average of `cleaning_facility` variable have the lowest results such as 3,62 (if rounded by 2), followed by `neat_furniture_placement` with result of the average is 3,69. These both variable are the weak point for cleanliness aspect. This weaknesses also affecting the total average score of cleanliness (could be found at "Analysis" tab) to be the lowest among all existing aspects.

Both of those variable have a high standard deviation (sd > 0,5) which indicate that the distribution was quite wide among the respondents' answers. Moreover, there was a change in the location of the cafeteria during the collection of the questionnaire results, it might affect the wide response that has mentioned before.

```{r product-stat-plot}
plot_product_stat <- ggplot(product_df, aes(x = variable, y = mean, fill = category))+
  geom_col() +
  coord_flip() +
  facet_wrap(~ aspect, scales = "free_y") +
  labs(title = "Average Score per Variable on Product Aspect",
       x = "Variable", y = "Mean Score") +
  scale_fill_manual(values = c("Needs Improvement" = "#FF9D23", 
                               "Medium" = "#B4E50D", 
                               "Good" = "#78C841")) +
  theme_minimal()
  
ggplotly(plot_product_stat)
#show(plot_product_stat)
```

##### **Product**  
In Product aspect, there are two different variables that fell into "Medium" category, such as `affordable_price` with the average of 3,65 and `price_vs_quality` with an average of 3,88. The `affordable_price` variable had a high standard deviation (\~0,93), this indicates a fairly wide spread among respondents' answers and may be influenced by various segments available.


```{r service-stat-plot}
plot_service_stat <- ggplot(services_df, aes(x = variable, y = mean, fill = category))+
  geom_col() +
  coord_flip() +
  facet_wrap(~ aspect, scales = "free_y") +
  labs(title = "Average Score per Variable on Service Aspect",
       x = "Variable", y = "Mean Score") +
  scale_fill_manual(values = c("Needs Improvement" = "#FF9D23", 
                               "Medium" = "#B4E50D", 
                               "Good" = "#78C841")) +
  theme_minimal()
  
ggplotly(plot_service_stat)
#show(plot_service_stat)
```

##### **Services**  
Finally, most respondents stated that service aspects fell into the “Good” category, as seen from the average of each variable, which was greater than 4 (“Agree” on the Likert scale) and the consistency of respondents (median) answering 4 on most service aspects. However, despite the ratings falling into the “Good” category, `staff_response` falls into the “Medium” category, as not all respondents felt that the staff in the cafeteria were responsive to questions or complaints.  

#### **Table View**  
```{r table-view-weaknesses-aspect}
#head(df_stats)
datatable(df_stats, caption = "Statistic Descriptive of Each Variables Based on Their Aspects")
```

### **Segmentation Based on Home Campus**  
This analysis was conducted to gain insight into the responses of respondents from various campuses regarding three aspects that influence student satisfaction with the University cafeteria.

```{r checking-home-campus-var, results='hide'}
#check unique value in home campus
unique(df$home_campus)

#check how many respondent who inserted "campus gj"
sum(df$home_campus == "campus gj", na.rm = TRUE)
```

```{r segmentation-home-campus}
segment_satis_scheme <- c(
  "Bad" = "#F93827",
  "Quite Bad" = "#FF9D23",
  "Good" = "#B4E50D",
  "Excellent" = "#78C841"
) 

#plot to count segmentation satisfaction 
plot_segment_satis <- ggplot(df, aes(x = home_campus, fill = satisfaction_category))+
  geom_bar()+
  labs(
    title = "Satisfaction per Home Campus Segmentation",
    x = "Home Campuses",
    y = "Count"
  )+
  scale_fill_manual(values = segment_satis_scheme)

#show(plot_segment_satis)
ggplotly(plot_segment_satis)
```

***Explanations:***\
Based on home campus segmentation, the majority of students from **Campus B and Campus S have a satisfaction category classified as “Good,”** with a few of them falling into the “Excellent” category. On the other hand, some respondents from **Campus S fall into the “Quite Bad”** review category, which may be due to their lowered expectations regarding the University canteen. Based on the above results, although satisfaction levels are relatively stable, there is **room for improvement to make the experience truly exceptional.**

### **Average Score per Aspect Grouped by Home Campus**{.tabset}  
This analysis was conducted to determine the level of satisfaction of respondents from different home campuses with regard to the three aspects of the cafeteria.
```{r mean-satis-aspect-per-home-campus, results= 'hide'}
#duplicate the df to new dataframe focusing on mean score per home campuses
mean_satisfaction_home_campus <- df %>%
  group_by(home_campus) %>%
  summarise(
    responses = n(),
    service_sd = sd(rowMeans(select(cur_data(), all_of(cols_services)), na.rm = TRUE), na.rm = TRUE) %>% round(3),
    cleanliness_sd = sd(rowMeans(select(cur_data(), all_of(cols_cleanliness)), na.rm = TRUE), na.rm = TRUE) %>% round(3),
    product_sd = sd(rowMeans(select(cur_data(), all_of(cols_product)), na.rm = TRUE), na.rm = TRUE) %>% round(3),
    
    services_score = mean(mean_services_score) %>% round(digits = 3),
    cleanliness_score = mean(mean_cleanliness_score) %>% round(digits = 3),
    product_score = mean(mean_product_score) %>% round(digits = 3),
    overall_score = mean(mean_satisfaction_score) %>% round(digits = 3)
  )

#make the df to long format
long_mean_satisfaction_home_campus <- mean_satisfaction_home_campus %>%
  pivot_longer(cols = c(services_score, cleanliness_score, product_score), names_to = "aspect", values_to = "score")

#Binning the score
long_mean_satisfaction_home_campus <- long_mean_satisfaction_home_campus %>% mutate(
  category = case_when(
     score > 4 ~ "Exellent",
     score >= 3.9 ~ "Good",
     TRUE ~ "Needs Improvement"
  )
)
```

#### **Graph View**
```{r plot-satis-aspect-per-home-campus}
#make a color scheme
mean_satisfaction_home_campus_scheme <- c(
  "services_score" = "#FF9D23",
  "cleanliness_score" = "#B4E50D",
  "product_score" = "#78C841"
) 

plot_satis_aspect_per_home_campus <- ggplot(long_mean_satisfaction_home_campus, aes(x = home_campus, y = score, fill = aspect)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average Score per Aspect by Home Campus",
       x = "Home Campus", y = "Score") +
  scale_fill_manual(values = mean_satisfaction_home_campus_scheme) +
  theme_minimal()

#show(plot_satis_aspect_per_home_campus)
ggplotly(plot_satis_aspect_per_home_campus)
```

**Main Insight:**

1.  **The Service aspect** (services_score) consistently received the highest score across all campuses, with the highest score belonging to Campus M (4.112) and the lowest to Campus GJ (4.000).\
2.  **Cleanliness** (cleanliness_score) shows the greatest difference between campuses:\
    2.1. *Highest score:* Campus M (4.008)\
    2.2. *Lowest score:* Campus S (3.754), this score also caused this campus to be the only one in the “Needs Improvement” category in the previous analysis.\
3.  **Products** (product_score) tend to be in the middle, relatively consistent with small differences between campuses (\~0.1).

***Explanation for Campus GJ:*** The graph above shows a comparison of scores for each aspect of the University cafeteria assessment, grouped by home campuses. Some of the data above cannot be confirmed for accuracy, particularly for respondents from the Campus GJ campus, as there was only one respondent who scored a 4 on all three aspects. Therefore, the results of respondent from greater jakarta should not be used as a basis for decision-making.

#### **Table View**
```{r showing-aspect-score-groupby-homecampus}
#head(mean_satisfaction_home_campus)
datatable(mean_satisfaction_home_campus, caption = "Aspects Score Group by Home Campus")
```

### **Segmentation Based on Major**{.tabset}

This analysis was conducted to gain insight into the average satisfaction scores of students grouped by major. Therefore I'll check the unique values in case there were so many majors are in the datasets.

```{r checking-major-var}
#check unique value in home campus
unique(df$major)
```

There are 12 unique values in major that might require to turn them into a broad categories. For example:

-   **Tech / IT:** Computer Science, Software Engineering, AI, Cyber Security, Computer Engineering, Data Science, Information Systems\
-   **Design / Creative:** Interior Design, Game Application\
-   **Business / Comm:** Digital Business, Marketing Comm, Public Relations

```{r make-grouped-major}
df <- df %>% mutate(
  major_group = case_when(
    major %in% c("computer science", "computer science - software engineering", "artificial intelligence", "data science", "cyber security", "computer engineering", "information systems") ~ "Tech",
    major %in% c("game application and technology", "interior design") ~ "Design",
    major %in% c("digital business", "communication - marketing communication", "public relations") ~ "Business/Communication",
    TRUE ~ "others"
  )
) 

#export to csv file
export_major_grouped_df <- df
write.csv(export_major_grouped_df, "5th_grouped_major_added_questionnaire_results.csv", row.names = FALSE)
```

```{r mean-satis-aspect-per-major, results='hide'}
#duplicate the df to new dataframe focusin on mean score per major
mean_satisfaction_major <- df %>%
  group_by(major_group) %>%
  summarise(
    responses = n(),
    services_score = mean(mean_services_score) %>% round(digits = 3),
    service_sd = df %>% select(all_of(cols_services)) %>% rowMeans(na.rm = TRUE) %>% sd(na.rm = TRUE) %>% round(3),
    
    cleanliness_score = mean(mean_cleanliness_score) %>% round(digits = 3),
    cleanliness_sd = df %>% select(all_of(cols_cleanliness)) %>% rowMeans(na.rm = TRUE) %>% sd(na.rm = TRUE) %>% round(3),
    
    product_score = mean(mean_product_score) %>% round(digits = 3),
    product_sd = df %>% select(all_of(cols_product)) %>% rowMeans(na.rm = TRUE) %>% sd(na.rm = TRUE) %>% round(3),
    
    overall_score = mean(mean_satisfaction_score) %>% round(digits = 3)
    )

#make the df to long format
long_mean_satisfaction_major <- mean_satisfaction_major %>%
  pivot_longer(cols = c(services_score, cleanliness_score, product_score), names_to = "aspect", values_to = "score")

#Binning the score
long_mean_satisfaction_major <- long_mean_satisfaction_major %>% mutate(
  category = case_when(
     score > 4 ~ "Exellent",
     score >= 3.9 ~ "Good",
     TRUE ~ "Needs Improvement"
  )
)
```

#### **Graph View**  
```{r plot-satis-aspect-per-major}
#make a color scheme
mean_satisfaction_major_scheme <- c(
  "services_score" = "#FF9D23",
  "cleanliness_score" = "#B4E50D",
  "product_score" = "#78C841"
) 

plot_satis_aspect_per_major <- ggplot(long_mean_satisfaction_major, aes(x = major_group, y = score, fill = aspect)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average Score per Aspect by Grouped Majors",
       x = "Home Campus", y = "Score") +
  scale_fill_manual(values = mean_satisfaction_major_scheme) +
  theme_minimal()

#show(plot_satis_aspect_per_major)
ggplotly(plot_satis_aspect_per_major)
```


***Insights & Explanations:***\
Based on the segmentation of grouped majors, students from the Tech field dominate the respondent population (n = 95), making the scores from this group the most representative reference.

On the other hand, the Design and Business/Communication groups showed relatively higher satisfaction scores. However, due to the very small number of respondents (n = 2 and n = 5), these results are not sufficiently robust to be generalized. This finding underscores **the importance of balanced representation in surveys to ensure that the analysis reflects the entire student population.**

#### **Table View**
```{r showing-aspect-score-grouped-majors}
#head(mean_satisfaction_major)
datatable(mean_satisfaction_major, caption = "Aspects Score by Grouped Majors")
```


## **Conclusions**\ 
The analysis shows that student satisfaction levels vary widely in every aspect. The previous analysis stated that most respondents answered the questionnaire within 2 minutes, which indirectly shows the seriousness of the respondents in filling out the questionnaire. From the analysis of the cafeteria assessment based on each aspect, there are two aspects that must be given special attention, namely cleanliness and product. Based on the analysis results, there is a significant spread in the aspects of cleanliness and product, where students have diverse answers based on their home campus and major category.

### **Summary of Key Findings**\
Some ***key points*** are achieved from previous analysis that are described as follows:

- Majority of respondents are dominated by student in tech field, showing analysis results based on the perspective of tech students.\
- Cleanliness aspect had the lowest average score compared with the others. This showed us that cleanliness must be prioritized with such development.\
- The variation range of responses are quite big, showed by some of the variable (e.g., cleaning_facility) had more than 0.5 (~0.96) for standard deviation. This variation is affected due to canteen that changes location during the survey period.\    
- Home campus segmentation show a significant differences between average score. This clearly showed that student from Campus S dominates the questionnaire respond with a bit high on variability (sd = ~0.57 until ~0.67).\

### **Prioritized Aspect for Improvement**\
In these three aspects (Service, Cleanliness, Product), there are some variables that had a space for improvement which will be explained as follows:\

#### **Cleanliness**\
Cleanliness aspect have the lowest average score by ~3.88 and **fell onto "Need Improvement"** category. This aspect has several variables related to it score. The following variables **fell into the "Medium" category** with plenty of room for improvement in terms of canteen performance in the cleanliness aspect:\

```{r calling-variable-aspects-clean}
ggplotly(plot_clean_stat)
```


**Prioritized Variable for Cleanliness**\

- cleaning_facility ("The cafeteria provides facilities such as sinks, tissues, and adequate hand washing facilities.")\
- neat_furniture_placement ("The layout and arrangement of tables/chairs in the cafeteria ensure orderly queues.")\
- cozy_seating_area ("The cafeteria has a comfortable and adequate seating area.")\
- cozy_room_layout ("The layout and arrangement of chairs and dining tables create a comfortable atmosphere in the cafeteria.")\
- clean_area ("The cafeteria area is clean and well organized.")\
- clean_utensils ("The cleanliness of eating utensils (plates, glasses, spoons, etc.) is maintained.")\

#### **Product**\
Despite cleanliness aspect who had the lowest avg.score, there is **product** aspect that has slight higher avg. score and fell onto "Medium" category. As explained before, each aspect had its own variables that fell into **"Medium" category** with a room for improvement of product aspect.

```{r calling-variable-aspects-product}
ggplotly(plot_product_stat)
```

**Prioritized Variable for Product**\

- price_vs_quality ("The taste of the food/drinks in the cafeteria is as expected.")\
- affordable_price ("The prices of food and drinks in the cafeteria are affordable for students.")\

#### **Services**\
At last, service aspect who had the highest avg. score. Despite being the highest, this aspect also need a bit of change in one variable in order to upgrade the quality of cafeteria services. The mentioned variable is explained below:\

```{r calling-variable-aspects-service}
ggplotly(plot_service_stat)
```

**Prioritized Variable for Services**\

- staff_response ("Canteen staff respond promptly when receiving orders or complaints.")

### **Main Recommendation**\
The cafeteria has weaknesses in terms of cleanliness and the product it offers. In order to confront this challenges, some changes need to be prioritized in both aspects who had some variables fell onto "Medium" category. Some recommendations are offered to help the improvement of canteen visitors satisfaction level, which will be explained below:\

- **Standarize Cleanliness Facility**\
  - ***Target:*** Cleanliness Aspect\
  - ***Reason Behind it:*** Cleanliness aspect has the lowest total average score among the others, and it variables has all variations surpassing 0.5. Especially in the cleaning_facility variable, this shows differences in students experience between canteen shifts.\  

- **Product Quality and Price Control**\
  - ***Target:*** Product Aspect\
  - ***Reason Behind it:*** Some variable is fell into "Medium" category (e.g., price_vs_quality, affordable_price), which leads to room for an improvement for an offered product. The analysis results from variables such as price_vs_quality show that the **perception of value-for-money is still weak** and inconsistent among respondents.\  

- **Equalizing Standard at Each Campus**\
  - ***Target:*** All Aspect\
  - ***Reason Behind it:*** Segmentation analysis has showed a significant differences in average scores (e.g., Campus S have the highest variations). Meanig that service and facility standards need to be harmonized so that the student experience is more consistent. \  

### **Steps for Implementations**
Every plan need an execution steps to accomplish the changes for improvement. This action plan may useful for some period of time such as:\

#### **Short Term (1 - 3 month)**\
- **Audit and Manual Monitoring**\  
  - Apply some checklist of daily cleaning inspections for tables, chairs, and utensils.\
  - Add cleaning support staff during busy hours (e.g., lunch).\
  
- **Quick Roll Call**\  
  - Morning roll call and every shift change in private with cleaning staff to ensure the hygiene standard & customer service are on track.\
  
- **Product Adjustment**\  
  - Putting a QR codes next to food/snack shelf to obtain reviews directly from consumers.\
  - Quick review for a new product in cafeteria, for example: give a quick rate from 1 to 5 and short statements like "Food worth the price.", "The food is fresh when it gets to you.", etc.)\

#### **Medium Term (3 - 6 month)**\
- **Equalizing Standard at Every Campus**\  
  - Establish SOPs (Standard Operating Procedures) for applying QR codes for quick reviews on new food shelves and encourage workers at morning roll call and shift change times to remind customers to fill out reviews every time they purchase new items. With this step, it'll be saving much more time to conducting an audit.\
  
#### **Long Term (6 - 12 month)**\
- **Infrastructure Improvement**\  
  - Seeing the varied responses of students regarding hygiene facilities, which indicate differences in facilities between cafeterias, it is necessary to make improvements to the infrastructure. This is important in order to provide comfort to students and ensure that they experience the same facilities regardless of the cafeteria location.\
  
- **Continuous evaluation**\  
  - Seeing the varied responses of students regarding hygiene facilities, which indicate differences in facilities between cafeterias, it is necessary to make improvements to the infrastructure. This is important in order to provide comfort to students and ensure that they experience the same facilities regardless of the cafeteria location.\
  
  
### **Closing: Expected impact**\
The implementation of the recommendations that have been formulated is expected to improve the consistency of hygiene standards, product quality, and uniformity of experience across campuses. With this step, student satisfaction levels can increase significantly while strengthening the image of the cafeteria as a facility that is comfortable, hygienic, and meets student needs.\


